Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-05 main.tex
mention simexpal as manager of experiments

    All algorithms are implemented in C++ and compiled with g++ (v.11.2.0).
    The experiments are executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available for review under \url{TODO:insert link}.

@@

    \bibliographystyle{apalike}
    \bibliography{references}

>>>>

    All algorithms are implemented in C++ and compiled with g++ (v.11.2.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available for review under \url{TODO:insert link}.

@@

    \bibliographystyle{IEEEtran}
    \bibliography{references}
